Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-21 paper/current/main.tex
update text with new figure

>>>>

%
% Figure - SemAxis results
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
	\caption{
		\textbf{Lengh of organization vectors captures the reach of organizations.}
		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
		The L2 norm corresponds to the distance to the origin of the vector space.
		Color indicates the rank of the university from the Times ranking, with 1 being the highest rank university.
		Uncolored points are universities without a times rank.
		A "boomerang"-shape emerges, wherein larger universities are more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm). 
		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
		The L2 norm is correlated weakly with the expected reach or organizations, that is, the number of total flows an organization has with others given its size ($R^{2} = 0.17$, \textbf{inset});
		The red line is the line of best fit.
	}
	\label{fig:semaxis}
\end{figure}
